Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring

### 2020-06-01 manuscript.Rmd
Formatting and typos

All scripts used for scrapping tweets and compressing data can be found at https://github.com/chbrown/twilight.

@@

For both the target only and the target and source data described above, time series of
the count of all events were generated by summing the total number of events
on each day, irrespective of ICEWS score. Similarly, time series of count
of positive events were generated by summing the number of ICEWS events
for each day that had an intensity rating greater than zero. Lastly,
time series of count of negative events were generated by summing the number
of ICEWS events for each day that had an intensity rating less than zero.

@@

# build table
pander(target_results, caption = "\\label{table-1}CRQA results for target only data.")

@@

The above-chance levels of determinism and recurrence rate demonstrate
the coupling of social cohesion to both total and negative events during
times of strife. During this period, 
the modal ICEWS event for each day (Figure \@ref(fig:plot-mode-event))
during May 1st---15th was almost consistently -10, the most violent 
event category. These dates directly correlate with the above-chance RR and DET
metrics for the WCRQA of social cohesion and count of negative events.
Furthermore, for WCRQA of social cohesion and positive event count during
this time period, DET was entirely within chance (Figure
\@ref(fig:plot-wcrqa-targ-all)). This supports our hypothesis, as the
positive events are seemingly not coupled with the social cohesion on Twitter
during civil uprisings during the Arab Spring.

>>>>

All scripts used for scraping tweets and compressing data can be found 
at https://github.com/chbrown/twilight.

@@

For both the target-only and the target and source data described above, time series of
the count of all events were generated by summing the total number of events
on each day, irrespective of ICEWS score. Similarly, time series of count
of positive events were generated by summing the number of ICEWS events
for each day that had an intensity rating greater than zero. Lastly,
time series of count of negative events were generated by summing the number
of ICEWS events for each day that had an intensity rating less than zero.

@@

# build table
pander(target_results, caption = "\\label{table-1}CRQA results for target-only data.")

@@

The above-chance levels of determinism and recurrence rate demonstrate
the coupling of social cohesion to both total and negative events during
times of strife. During this period, 
the modal ICEWS event for each day (Figure \@ref(fig:plot-mode-event))
during May 1st--15th was almost consistently -10, the most violent 
event category. These dates directly correlate with the above-chance RR and DET
metrics for the WCRQA of social cohesion and count of negative events.
Furthermore, for WCRQA of social cohesion and positive event count during
this time period, DET was entirely within chance (Figure
\@ref(fig:plot-wcrqa-targ-all)). This supports our hypothesis, as the
positive events are seemingly not coupled with the social cohesion on Twitter
during civil uprisings during the Arab Spring.
